### 2013-05-29 inst/examples/adp-intro.Rmd

$$V_t(S_t) = \max_{x_t \in \chi_t} \left(C(S_t, x_t) + \gamma \sum_{s^{\prime} \in mathcal{S}} \mathbb{P}(s^{\prime} | S_t^n, x_t) V_{t+1}^{n-1} s^{\prime} \right)$$

@@

```{r}
N <- 5 # iterations
M <- 10 # gridsize 
Tmax <- 5 # Time horizon

@@

chi <- seq(0, 1, length.out = M)
S <- seq(0, 1, length.out = M)

@@

V <- matrix(rep(chi, Tmax), nrow=M) # matrix(0, M, Tmax)
X <- matrix(0, M, Tmax)
C <- function(S, X) pmin(S, X)
S_0 <- 0.5

@@

  omega_n <- rlnorm(Tmax, 0, sigma_g)
  S_current  <- S_0

  for(t in 1:(Tmax-1)){

    # index of the state we're considering
    s <- which.min(abs(S-S_current)) 
    # Find the action maximizing the value
    values <- sapply(1:length(chi), function(x)
      C(S[s], chi[x]) + gamma * sdp_matrix[[x]][s,] %*% V[,t])
    hat <-  c(x_nt = which.max(values), v_nt = max(values))

    # Update value V 
    V[hat["x_nt"], t] <- hat["v_nt"]

    # Advance the state in time along random path  
    S_current <- omega_n[t] * f(S_current, chi[x_nt], p)
  }

}
```

>>>>

$$V_t(S_t) = \max_{x_t \in \chi_t} \left(C(S_t, x_t) + \gamma \sum_{s^{\prime} \in \mathcal{S}} \mathbb{P}(s^{\prime} | S_t^n, x_t) V_{t+1}^{n-1} s^{\prime} \right)$$

@@

```{r}
N <- 50000 # iterations
M <- 20 # gridsize 
Tmax <- 5 # Time horizon

@@

sigma_g <- 0.5 # larger variation in random draws helps
chi <- seq(0, 1, length.out = M)
S <- seq(0, 1, length.out = M)

@@

V <- matrix(0, M, Tmax) # matrix(rep(chi, Tmax), nrow=M) # 
V[,1] <- chi   # fails to explore if it doesn't have at least some non-zero values

C <- function(S, X) pmin(S, X)
S_0 <- 0.5 
alpha <- 1 # learning rate

@@

  omega_n <- rlnorm(Tmax, 0, sigma_g)
  S_current <- S_0 #runif(1,0,1) # explores faster when this is random

  for(t in 1:Tmax){
    # index of the state we're considering
    s <- which.min(abs(S-S_current))

    # Find the action maximizing the value
    values <- sapply(1:length(chi), function(x)
      C(S[s], chi[x]) + gamma * sdp_matrix[[x]][s,] %*% V[,t])
    hat <-  c(x_nt = which.max(values), v_nt = max(values))

    # Update value V as mixture of new value and previous value
    V[hat["x_nt"], t] <- (1 - alpha) * V[hat["x_nt"],t] + alpha * hat["v_nt"]

    # Advance the state in time along random path  
    S_current <- omega_n[t] * f(S_current, chi[hat["x_nt"]], p)

  }
}
```

for comparison: the SDP solution

```{r}
opt <- find_dp_optim(sdp_matrix, S, chi, 70, 0.5, C, 1-gamma, reward=0)
opt$V
```
